Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-24 draft.tex
some progress
gather material on potential reconstruction

>>>>

\newpage\color{red}
 We want 
    \| w_{m} \|_{L^{p}(T_m)}^{p}
        1 
        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
    \right)^{p/q}
        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
 In the special case $p=1$ and $p=\infty$,
    \| w_{m} \|_{L^{1}(T_m)}
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
    \| u_{F_m} \|_{L^{1}(U_{F_m})}
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
    \| w_{m-1}\|_{L^{1}(T_{j(m)})}
    \| w_{m} \|_{L^{2}(T_m)}^{2}
        1 
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \| u_{F_m} \|_{L^{2}(T_m)}^{2}
        \| u_{F_{m}} \|_{L^{2}(T_{j(m)})}^{2}
        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
    \| w_{m} \|_{L^{\infty}(T_m)}
    3
    \max\left( 
        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
 \color{orange}
    \| w_{m} \|_{L^{p}(T_m)}^{p}
        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
    \right)^{p/q}
        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
 In the special case $p=1$ and $p=\infty$, 
    \| w_{m} \|_{L^{1}(T_m)}
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
    \| u_{F_m} \|_{L^{1}(U_{F_m})}
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
    \| w_{m-1}\|_{L^{1}(T_{j(m)})}
    \| w_{m} \|_{L^{2}(T_m)}^{2}
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \| u_{F_m} \|_{L^{2}(T_m)}^{2}
        \| u_{F_{m}} \|_{L^{2}(T_{j(m)})}^{2}
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
    \| w_{m} \|_{L^{\infty}(T_m)}
    3
    \max\left( 
        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
 \color{JungleGreen}
    \| w_{m} \|_{L^{p}(T_m)}^{p}
        3
    \right)^{p/q}
        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
        3
    \right)^{p/q}
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{p}(T_m \cup T_{j(m)})}^{p}
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
 In the special case $p=1$ and $p=\infty$, ????
    \| w_{m} \|_{L^{1}(T_m)}
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{1}(T_m \cup T_{j(m)})}^{1}
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \| w_{m-1}\|_{L^{1}(T_{j(m)})}^{1}
    \| w_{m} \|_{L^{2}(T_m)}^{2}
    3
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{2}(T_m \cup T_{j(m)})}^{2}
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
    \| w_{m} \|_{L^{\infty}(T_m)}
    3
    \max\left( 
        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
 \color{MidnightBlue}
    \| w_{m} \|_{L^{p}(T_m)}^{p}
        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
    \right)^{p/q}
        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
    \right)^{p/q}
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{p}(T_m \cup T_{j(m)})}^{p}
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
 In the special case $p=1$ and $p=\infty$, ????
    \| w_{m} \|_{L^{1}(T_m)}
    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{1}(T_m \cup T_{j(m)})} 
        \| w_{m-1}\|_{L^{1}(T_{j(m)})} 
    \| w_{m} \|_{L^{2}(T_m)}^{2}
        \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{2}(T_m \cup T_{j(m)})}^{2}
        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
    \| w_{m} \|_{L^{\infty}(T_m)}
    3
    \max\left( 
        \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
        \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}

 We introduce the operator $B^{k}$, which can be written in several alternative forms
\begin{align*}
    B^{k} u(x) 
    &= 
    - |\Omega|^{-1}
    \int_{\Omega} \,(x-a) \lrcorner \int_1^\infty t^{{k}-1}\,u\left( a+t(x-a) \right) \,dt\,da
    \\&= 
    |\Omega|^{-1}
    \int_{\Omega} \,(x-a) \lrcorner \int_0^1 t^{-{k}-1}\,u\left( a+(x-a)/s \right) \,ds\,da
    .
\end{align*}
If $u \in C^{\infty}_{c}(\bbR^{n},\Alt^{k})$, 
then $B^{k} u$ is smooth with support in $\bbR^{n}\setminus\overline\Omega$ and $B^{k} u(x) = 0$ when $x \notin \Omega$. 
Since $\Omega$ is convex, $u \in C^{\infty}_{c}(\Omega,\Alt^{k})$ implies $\supp B^{k} u \subset\Omega$, 
Since $\Omega$ is bounded, $\supp u \subseteq \overline\Omega$ implies $\supp B^{k} u \subset\overline\Omega$. 
% The fact that $B^{k}$ indeed maps 
% $C^{\infty}_{c}(\bbR^{n},\Alt^{k})$ to $C^{\infty}_{c}(\bbR^{n},\Alt^{{k}-1})$ will be a the following theorem.

\begin{align*}
    \int_{\Omega}
    \left| B^{k} u(x) \right|^{p}
    dx
    &
    = 
    |\Omega|^{-1}
    \int_{\Omega}
    \int_{\Omega} 
    \int_0^1
    s^{(-{k}-1)p}\, |x-a|^{p} \left| u\left( a+(x-a)/s \right) \right|^{p} \,ds\,da
    dx
    \\&
    = 
    |\Omega|^{-1}
    \int_{\Omega}
    \int_{\Omega-a} 
    \int_{|z|/D}^{1}
    s^{(-{k}-1)p}\, |z|^{p} \left| u\left( a+z/s \right) \right|^{p} \,ds\,da
    dz
    \\&
    = 
    |\Omega|^{-1}
    \int_{\Omega}
    \int_{2\Omega} 
    \int_{|z|/D}^{1}
    s^{(-{k}-1)p}\, |z|^{p} \left| u\left( a+z/s \right) \right|^{p} \,ds\,da
    dz
    \\&
    = 
    |\Omega|^{-1}
    \int_{\Omega + z/s}
    \int_{2\Omega} 
    \int_{|z|/D}^{1} % y = a + z/s
    s^{(-{k}-1)p}\, |z|^{p} \left| u\left( y \right) \right|^{p} \,ds\,dy
    dz
    \\&
    = 
    |\Omega|^{-1}
    \int_{2\Omega}
    \int_{2\Omega} 
    \int_{|z|/D}^{1} % y = a + z/s
    s^{(-{k}-1)p}\, |z|^{p} \left| u\left( y \right) \right|^{p} \,ds\,dy
    dz
    .
\end{align*}

\begin{align*}
    G_\ell(x,y) 
    &\leq 
    \int_{0}^{\frac{D}{|x-y|}} \tau^{n-\ell} (\tau+1)^{\ell-1} \,d\tau
    \\
    &\leq 
    \frac{|x-y|}{D}
    \int_{0}^{\frac{D}{|x-y|}} \frac{D}{|x-y|} \tau^{n-\ell} (\tau+1)^{\ell-1} \,d\tau
    .
\end{align*}
\begin{align*}
    G_\ell(x,y)^{p} 
    &\leq 
    \frac{|x-y|}{D}
    \int_{0}^{\frac{D}{|x-y|}} \frac{D^{p}}{|x-y|^{p}} \tau^{pn-p\ell} (\tau+1)^{p\ell-p} \,d\tau
    \\&\leq 
    \frac{|x-y|}{D}
    \frac{D^{p}}{|x-y|^{p}} \int_{0}^{\frac{D}{|x-y|}} (\tau+1)^{pn-p} \,d\tau
    \\&\leq 
    \frac{D^{p-1}}{|x-y|^{p-1}} \left( \left( \frac{D}{|x-y|} + 1 \right)^{pn-p+1} - 1 \right)
    \\&\leq 
    \frac{D^{p-1}}{|x-y|^{p-1}} \left( 2^{pn-p+1} \left( \frac{D}{|x-y|} \right)^{pn-p+1} - 1 \right)
    \\&\leq 
    2^{pn-p+1} \frac{D^{pn}}{|x-y|^{pn}} - \frac{D^{p-1}}{|x-y|^{p-1}}
    .
\end{align}

Moreover,  
\begin{align*}
    \int_{\Omega} \left| B_{\ell} u(x) \right|^{p} dx
    &=
    |\Omega|^{-1} 
    \int_{\Omega} 
    \int_{\Omega} 
    \left( 2^{pn-p+1} \frac{D^{pn}}{|x-y|^{pn}} - \frac{D^{p-1}}{|x-y|^{p-1}} \right)
    \left| (x-y)\lrcorner u(y) \right|^{p} 
    dy dx
    \\&=
    |\Omega|^{-1} 
    \int_{\Omega} 
    \int_{\Omega} \left( 2^{pn-p+1} D^{pn} |x-y|^{-pn+p} - D^{p-1} |x-y| \right) dx
    \left| u(y) \right|^{p} 
    dy
    .
\end{align*}

We use the radial integrals
\begin{align*}
    \int_{B_D(0)} |z|^{m} dz
    =
    \vol_{n-1}(S_1) \int_0^D r^{m} r^{n-1} dr
    =
    \vol_{n-1}(S_1) \int_0^D r^{m+n-1} dr
    =
    \vol_{n-1}(S_1) \frac{D^{m+n}}{m+n}
    .
\end{align*}

### 2024-06-24 main.tex
gather material on potential reconstruction

\subsection{Inequalities for partial boundary conditions on a single simplex}

We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
such that the $i$-th coordinate equals zero along $\hat F_i$.

% Copied from McIntosh paper 
We begin with introducing the Costabel-McIntosh-Bogovski\u{\i} kernel.
For $\ell\in\{0,\dotsc,n\}$, we define the kernel $G_\ell : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}
\label{eq:Gl}
  G_\ell(x,y) = 
  \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt \;.
\end{equation}
Given a differential form $u \in {C^\infty}_0(\bbR^n,\Alt^\ell)$, \(1\leq \ell \leq n\), 
we then define the integral operators
\begin{align}
  T_\ell u(x) &= \int G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
\end{align}
We call $T_\ell$ a Bogovski\u{\i}-type operator.

In order to see that the integrals in the definition of $T_\ell$ exist, 
we first rewrite the kernel $G_\ell$:
\begin{align*}
    G_\ell(x,y) 
    &= 
    \int_0^\infty \tau^{n-\ell} (\tau+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+\tau(x-y) \right)\,d\tau
    \\
    &= 
    \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} 
    \int_0^\infty \tau^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+\tau(x-y) \right)\,d\tau 
    \\
    &= 
    |\Omega|^{-1}\sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \,
    |x-y|^{k-n} \int_0^\infty r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr \;
    .
\end{align*}
We can restrict the inner integrals to the range $0 \leq r \leq D$. Thus 
\begin{align*}
    G_\ell(x,y) 
    &\leq 
    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_0^D r^{n-k-1} \,dr \;.
    \\
    &= 
    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
\end{align*}
We pointwise estimate $B_{\ell} u(x)$ by the result of a convolution of a locally integrable function with $u$:
\begin{align*}
    \left| B_{\ell} u(x) \right|
    &=
    \left| 
        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \left| 
        \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \right| 
    \\&\leq 
    \left| 
        \int_{\bbR^{n}} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
    \right| 
    .
\end{align*}
We recall the radial integrals 
\begin{align*}
    \int_{B_D(0)} |z|^{k+1-n} dz
    =
    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
    =
    \vol_{n-1}(S_1) \int_0^D r^{k} dr
    =
    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
    .
\end{align*}
We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
    \\&
    =
    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
    %\\&
    =
    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A(n,\ell) \leq 2^{\ell-1}}
    .
\end{align*}
So the convolution of $u$ is taken against an integrable function. 
Taylor's inequality now implies: 
\begin{align*}
    \| B_{\ell} u \|_{L^{p}(\Omega)}
    &\leq 
    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
In particular, we have a bounded operator $B_{\ell} : L^{p}(\bbR^n,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1})$ for any $1 \leq p \leq \infty$.

@@

Then we substitute $s = (t-1)/t$:
\begin{align*}
    &= 
    \int \int_1^\infty (t-1)^{n-\ell}t^{-n+\ell-1} 
    \chi_{\Omega}\left(a\right)
    \frac{(a-y)}{t} \lrcorner u(x+(a-x)/t) \,dt\,da 
    \\
    &= 
    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1-n-1} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u(x+(a-x)/t) \,dt\,da
    .
\end{align*}
Then we substitute $s = (t-1)/t$:
\begin{align*}
    T_\ell u(x) 
    &= 
    \int \int_1^\infty s^{n-\ell} (s-1)^{2} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( x+(s-1)(a-x) ) \frac{-1}{(s-1)^2}\,ds\,da
    \\
    &= 
    - \int \int_1^\infty s^{n-\ell} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( s(a-x) - a ) \,ds\,da
    \\
    &=
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_1^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
We copy a statement by McIntosh and Costabel, who are too fucking lazy to write down their goddamn substititions for fucks sake, stupid assholes:
\begin{align*}
    T_\ell u(x) 
    = 
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_1^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $T_\ell u(x)$ is smooth with support contained in $\overline\Omega$ as well.

@@

>>>>

\subsection{Bogovski\u{\i}-type operators}
We begin with introducing the Costabel-McIntosh-Bogovski\u{\i} kernel.
For $\ell\in\{0,\dotsc,n\}$, we define the kernel $G_\ell : \bbR^{n} \times \bbR^{n} \rightarrow \bbR$ by
\begin{equation}
\label{eq:Gl}
  G_\ell(x,y) = 
  \int_1^\infty (t-1)^{n-\ell}t^{\ell-1} |\Omega|^{-1}\chi_{\Omega} \left(y+t(x-y)\right)\,dt \;.
\end{equation}
Given a differential form $u \in {C^\infty}_0(\bbR^n,\Alt^\ell)$, \(1\leq \ell \leq n\), 
we then define the integral operators
\begin{align}
  T_\ell u(x) &= \int G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
\end{align}
We call $T_\ell$ a Bogovski\u{\i}-type operator.

In order to see that the integrals in the definition of $T_\ell$ exist, 
we first rewrite the kernel $G_\ell$:
\begin{align*}
    G_\ell(x,y) 
    &= 
    \int_0^\infty \tau^{n-\ell} (\tau+1)^{\ell-1} |\Omega|^{-1} \chi_{\Omega} \left( x+\tau(x-y) \right)\,d\tau
    \\
    &= 
    \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} 
    \int_0^\infty \tau^{n-k-1} |\Omega|^{-1} \chi_{\Omega}\left( x+\tau(x-y) \right)\,d\tau 
    \\
    &= 
    |\Omega|^{-1}\sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \,
    |x-y|^{k-n} \int_0^\infty r^{n-k-1} \chi_{\Omega}\left(x+r\frac{x-y}{|x-y|}\right)\,dr \;
    .
\end{align*}
We can restrict the inner integrals to the range $0 \leq r \leq D$. Thus 
\begin{align*}
    G_\ell(x,y) 
    &\leq 
    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \int_0^D r^{n-k-1} \,dr \;.
    \\
    &= 
    |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} |x-y|^{k-n} \frac{ D^{n-k} }{n-k}.
\end{align*}
We pointwise estimate $B_{\ell} u(x)$ by the result of a convolution of a locally integrable function with $u$:
\begin{align*}
    \left| B_{\ell} u(x) \right|
    &=
    \left| 
        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \left| 
        \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \right| 
    \\&\leq 
    \left| 
        \int_{\bbR^{n}} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
    \right| 
    .
\end{align*}
We recall the radial integrals 
\begin{align*}
    \int_{B_D(0)} |z|^{k+1-n} dz
    =
    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
    =
    \vol_{n-1}(S_1) \int_0^D r^{k} dr
    =
    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
    .
\end{align*}
We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
    \\&
    =
    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
    %\\&
    =
    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A(n,\ell) \leq 2^{\ell-1}}
    .
\end{align*}
So the convolution of $u$ is taken against an integrable function. 
Taylor's inequality now implies: 
\begin{align*}
    \| B_{\ell} u \|_{L^{p}(\Omega)}
    &\leq 
    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
    \leq 
    n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
In particular, we have a bounded operator $B_{\ell} : L^{p}(\bbR^n,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1})$ for any $1 \leq p \leq \infty$.

@@

Then we substitute $s = (t-1)/t$:
\begin{align*}
    &= 
    \int \int_1^\infty (t-1)^{n-\ell}t^{-n+\ell-1} 
    \chi_{\Omega}\left(a\right)
    \frac{(a-y)}{t} \lrcorner u(x+(a-x)/t) \,dt\,da 
    \\
    &= 
    \int \int_1^\infty (t-1)^{n-\ell}t^{\ell-1-n-1} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u(x+(a-x)/t) \,dt\,da
    .
\end{align*}
Then we substitute $s = (t-1)/t$:
\begin{align*}
    T_\ell u(x) 
    &= 
    \int \int_1^\infty s^{n-\ell} (s-1)^{2} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( x+(s-1)(a-x) ) \frac{-1}{(s-1)^2}\,ds\,da
    \\
    &= 
    - \int \int_1^\infty s^{n-\ell} \chi_{\Omega}\left(a\right)\, (x-a)\lrcorner u( s(a-x) - a ) \,ds\,da
    \\
    &=
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_1^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
We copy a statement by McIntosh and Costabel, who are too fucking lazy to write down their goddamn substititions for fucks sake, stupid assholes:
\begin{align*}
    T_\ell u(x) 
    = 
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_1^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
$a = y + t(x-y)$
$s = \frac{t}{t-1}$
From that representation we can tell that whenever $u \in C^{\infty}(\bbR^{n})$ has support contained in $\overline\Omega$, we immediately have that $T_\ell u(x)$ is smooth with support contained in $\overline\Omega$ as well.

@@

\subsection{Inequalities for partial boundary conditions on a single simplex}
We let $\hat F_0$ be the convex closure of the first $n$ unit vectors. 
We let $\hat F_1, \dots, \hat F_n$ be the remaining faces of the reference simplex 
such that the $i$-th coordinate equals zero along $\hat F_i$.
